Local Adaptive Optimization of Time step

### 2013-10-08 report/report.tex
Added notes/start of method and playing around with the simulator for new methods

@@

\section{Introduction}
Simulations of large (order of millions of vertices) hyper elastic materials
are very time consuming. When working with materials of varying density of
vertices, the highest densities often make the most strict bounds on size of
the time step of the simulation in order to keep the materials (and grids)
stable. In a ``standard'' simulation with a global time step size we need
to compute possibly unnecessarily many computations on the coarser parts of
the material caused by this bound. When furthermore having materials with a
large amount of somewhat equally distributed vertices and smaller patches of
detailed areas with higher density of vertices, it would be an advantage to be
able to perform large time steps for the majority of the material and smaller
steps for the local patches when vertices cause instability. We call this
concept local adaptive optimization of time step, which we will study further
in this report.

@@

\section{Method}

\begin{align}
F_k &= -k \\
F_m &= -F
\end{align}

@@

>>>>

\providecommand{\abs}[1]{\left \lvert #1 \right \rvert}

@@

\section{Introduction}
Simulations of large (order of millions of vertices) hyper elastic materials
are very time consuming. When working with materials of varying density
of vertices, the highest densities often make the most strict bounds on
size of the time step of the simulation in order to keep the materials (and
grids) stable and the discretization correct. In a ``standard'' simulation
with a global time step size we need to compute possibly unnecessarily many
computations on the coarser parts of the material caused by this bound.
When furthermore having materials with a large amount of somewhat equally
distributed vertices and smaller patches of detailed areas with higher density
of vertices, it would be an advantage to be able to perform large time steps
for the majority of the material and smaller steps for the local patches when
vertices cause instability. We call this concept local adaptive optimization
of time step, which we will study further in this report.

@@

\section{Method}
We will in this report consider the 1 dimensional problem of simulating a mass
spring system, which is usually used for simulating cloth and hair etc. A mass
spring system is a system consisting of a set of vertices $V$ each having a
specified mass $m$, force $F$ and velocity $u$ and a set of springs $S$ with two
endpoints $p_f \in V$ and $p_t \in V \setminus p_f$. Each spring has a damping
factor $d$, stiffness constant $K$ and rest length $l_0$ describing the state of
the spring.

Things to write about (notes):

Damping force $F_d$:
\begin{align*}
    \Delta l &= l_{left} - l_{right} \\
    F_d      &= - C_d v(i) =  - C_d \frac{\left(v_{left} - v_{right}\right)
\Delta l}{\abs{\Delta l}}
\end{align*}

Spring force $F_s$:
\begin{align*}
    F_s = kx = -k \left( l - l_0 \right)
\end{align*}

Explicit Euler method:
\begin{align*}
    x(t+h) &= x(t) + h \frac{\partial x(t)}{\partial t}
\end{align*}

Midpoint method:
\begin{align*}
    x(t+h) = x(t) + h \left( f \left(x + \frac{h}{2} f \left(t \right) \right) \right)
\end{align*}

@@

\subsection{Initial though}
Normal timestepping with switch detection and refinement

\subsection{Stepping with interpolation and lockout of re-calculations}
